Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-06-28 Paper/main.tex
Posili

\begin{figure}[H]
\caption{Covariate distribution in Historical and Pilot data}
\label{covariate_distribution}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \caption{Continuous variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_continuous.png}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Categorical variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_categorical.png}
        \end{subfigure}
    \end{center}
    {\footnotesize \textit{Notes: } Covariate distributions for historical -used to calibrate our calculator- and pilot data. All continuous variables are plotted in logs. Color guide is the same for both variable types.}
    {\footnotesize \textit{Script: } \texttt{covariate\_plots.R}}
\end{figure}

@@

\begin{figure}[H]
    \caption{Calculator treatment format (example)}
    \label{calc_template}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{calctreat.png}
        \end{center}
        {\footnotesize \textit{Notes: An example of the format shown to subjects in calculator treatment group. It shows some data on the worker, the minimum legal amount she deserves for different types of benefits, a small note on average trial durations, and calculator results: probability for each conclusion outcome, average duration and amount won (both conditional on each outcome).}}
\end{figure}

@@

\begin{figure}[H]
    \caption{ }
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{oos_fit_liqtotal.tiff}
     \end{subfigure}

        \begin{subfigure}{0.49\textwidth}    
         \centering
        \includegraphics[width=1\textwidth]{oos_fit_duracion.tiff}
     \end{subfigure}

     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{oss_fit_categorical.tiff}
     \end{subfigure}

        \end{center}
        {\footnotesize \textit{Notes: } }
        {\footnotesize \textit{R Script: } \texttt{}}
\end{figure}

>>>>

\begin{figure}[H]
\caption{Covariate distribution in Historical and Pilot data}
\label{covariate_distribution}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \caption{Continuous variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_continuous.tiff}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Categorical variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_categorical.tiff}
        \end{subfigure}
    \end{center}
    {\footnotesize \textit{Notes: } Covariate distributions for historical -used to calibrate our calculator- and pilot data. All continuous variables are plotted in logs. Color guide is the same for both variable types.}
    {\footnotesize \textit{Script: } \texttt{covariate\_plots.R}}
\end{figure}

@@

\begin{figure}[H]
    \caption{Calculator treatment format (example)}
    \label{calc_template}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{calctreat.png}
        \end{center}
        {\footnotesize \textit{Notes: An example of the format shown to subjects in calculator treatment group. It shows some data on the worker, the minimum legal amount she deserves for different types of benefits, a small note on average trial duration, and calculator results: probability for each conclusion outcome, average duration and amount won (both conditional on each outcome).}}
\end{figure}

@@

\begin{figure}[H]
    \caption{ }
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{oos_fit_liqtotal.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{oos_fit_categorical.tiff}
     \end{subfigure}

        \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes }
        {\footnotesize \textit{R Script: } \texttt{}}
\end{figure}

\begin{figure}[H]
    \caption{}
    \label{}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{oos_fit_duracion.tiff}
        \end{center}
        {\footnotesize \textit{Notes: }}
        {\footnotesize \textit{R Script: } \texttt{}}
\end{figure}
